### 2022-07-14 draft.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@5a150cb024075c3f4a0c0f293c3d3ba61fcf4ed8 🚀

In the Serengeti food web there is a positive relationship between the
out degrees of predators and the size of their ranges
(tbl.~\ref{tbl:everyone}). In addition, our results show that there is a
negative relationship between the relative loss of predators' ranges and
their number of preys (fig.~\ref{fig:degree}), reinforcing the idea that
generalist species can preserve their distributions longer while losing
interactions. The factors limiting the geographical range of a species
in a community can vary with connectivity and richness (Svenning et al.
2014). Younger communities may be more affected by environmental
limitations because they are dominated by generalist species, while
older metacommunities are probably affected in different ways in the
center of the distribution, at the edge of ranges, and in sink and
source communities (Svenning et al. 2014; Godsoe et al. 2017; Cazelles
et al. 2016; Bullock et al. 2000). Additionally, it is likely that
species with larger ranges of distribution and those that are more
generalists would co-occur with a greater number of other species
(Dáttilo et al. 2020), while dispersal capacity of competitive species
modulate their aggregation in space and the effect of interactions on
their range limits (Godsoe et al. 2017).

@@

The lack of superposition between IUCN range maps and GBIF occurrences
suggests that we certainly do miss geographical information about the
distribution of a certain species, but it is not an indicator of the
completeness of the information about ecological interactions. However,
if both GBIF and IUCN occurrences tend to superpose and still the
species is locally removed, this indicates we don't have information
about all its interactions. The combination of this rationale with our
method of updating range maps based on ecological interactions allows us
to have a clearer idea of which information we are missing. For example,
the lion (\emph{Panthera leo}) was one of the species with the smallest
difference between the original and the updated ranges
(fig.~\ref{fig:degree}), but 59.5\% of the GBIF occurrences for this
species fell outside the IUCN range (fig.~\ref{fig:gbif}). In this
particular case, the IUCN maps seem to agree with species interaction
data. However, the disagreement between the IUCN and the GBIF databases
is concerning and suggests that the IUCN maps might underestimate the
lion's distribution. On the other hand, \emph{Leptailurus serval} and
\emph{Canis mesomelas} are two of the three species that lose the higher
proportion of range due to the lack of paths to a herbivore
(fig.~\ref{fig:degree}), but are also some of the species with the
higher proportion of GBIF occurrences inside IUCN range maps
(fig.~\ref{fig:gbif}). This indicates that the information we are
missing for these two species is related to either the occurrence of an
interaction or the presence of interacting species. To illustrate that,
we mapped the GBIF data for the prey of \emph{Leptailurus serval}, with
a mobility buffer around each point (fig.~\ref{fig:serval}). When
considering GBIF data, approximately 53\% of the prey's occurrences are
within the portion of the serval's range that was lost. With the buffer
area, this corresponds to 13\% of the lost range. This means that by
adding GBIF information, we would reduce the loss of range (or
information) for the predator by 13\% since its distribution is
conditional on the occurrence of its preys.

>>>>

In the Serengeti food web there is a positive relationship between the
out degrees of predators and the size of their ranges. In addition, our
results show that there is a negative relationship between the relative
loss of predators' ranges and their number of preys, reinforcing the
idea that generalist species can preserve their distributions longer
while losing interactions. The factors limiting the geographical range
of a species in a community can vary with connectivity and richness
(Svenning et al. 2014). Younger communities may be more affected by
environmental limitations because they are dominated by generalist
species, while older metacommunities are probably affected in different
ways in the center of the distribution, at the edge of ranges, and in
sink and source communities (Svenning et al. 2014; Godsoe et al. 2017;
Cazelles et al. 2016; Bullock et al. 2000). Additionally, it is likely
that species with larger ranges of distribution and those that are more
generalists would co-occur with a greater number of other species
(Dáttilo et al. 2020), while dispersal capacity of competitive species
modulate their aggregation in space and the effect of interactions on
their range limits (Godsoe et al. 2017).

@@

The lack of superposition between IUCN range maps and GBIF occurrences
suggests that we certainly do miss geographical information about the
distribution of a certain species, but it is not an indicator of the
completeness of the information about ecological interactions. However,
if both GBIF and IUCN occurrences tend to superpose and still the
species is locally removed, this indicates we don't have information
about all its interactions. The combination of this rationale with our
method of updating range maps based on ecological interactions allows us
to have a clearer idea of which information we are missing. For example,
the lion (\emph{Panthera leo}) was one of the species with the smallest
difference between the original and the updated ranges, but 59.5\% of
the GBIF occurrences for this species fell outside the IUCN range
(fig.~\ref{fig:gbif}). In this particular case, the IUCN maps seem to
agree with species interaction data. However, the disagreement between
the IUCN and the GBIF databases is concerning and suggests that the IUCN
maps might underestimate the lion's distribution. On the other hand,
\emph{Leptailurus serval} and \emph{Canis mesomelas} are two of the
three species that lose the higher proportion of range due to the lack
of paths to a herbivore, but are also some of the species with the
higher proportion of GBIF occurrences inside IUCN range maps
(fig.~\ref{fig:gbif}). This indicates that the information we are
missing for these two species is related to either the occurrence of an
interaction or the presence of interacting species. To illustrate that,
we mapped the GBIF data for the prey of \emph{Leptailurus serval}, with
a mobility buffer around each point (fig.~\ref{fig:serval}). When
considering GBIF data, approximately 53\% of the prey's occurrences are
within the portion of the serval's range that was lost. With the buffer
area, this corresponds to 13\% of the lost range. This means that by
adding GBIF information, we would reduce the loss of range (or
information) for the predator by 13\% since its distribution is
conditional on the occurrence of its preys.
